### 2019-07-15 manuscript/methods.tex
fixing the number of states (figure and methods)

Matching our character state data to the largest time-calibrated phylogeny of Solanaceae \citep{sarkinen_2013} yielded 651 species with ploidy and/or breeding system information on the tree.
% FIXME: Rosana will update numbers around here TODO:STILL NOT CORRECT!!!
Of these, 290 had information for both states.
The number of species in each combination of states is summarized in \cref{figure:stateclassifications}A.
We retained all 651 species in each of the analyses below because pruning away tips lacking breeding system in the ploidy-only analyses (and vice versa) would discard data that could inform the diversification models.
A total of 405 taxa without any information about breeding system or ploidy were excluded.
%Tips without trait data might not improve point estimation of diversification parameters while increasing uncertainty in the estimates of trait linked diversification
% R-This is very important but I have removed it because I think it is a full on paper by its own
%Including this many more species would have prohibitively slowed our analyses, especially those implementing the most complex models.

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{states} % FIXME: update numbers
\caption{
Character states used for each of the models.
Each species retained on the tree belonged to one of five possible categories, depending on whether ploidy and/or breeding system were known.
(A) The five categories and the number of species in each.
Abbreviations are $I$ for self-incompatible, $C$ for self-compatible, $D$ for diploid, $P$ for polyploid, $?$ for unknown.
Because polyploidization breaks this form of self-incompatibility, SI species with unobserved ploidy ($I?$) are taken to be diploid ($ID$), and polyploid species with unobserved breeding system ($?P$) are taken to be SC.
(B) Category groupings into states for each model type.
For example, there are 34 species that are SC with unknown ploidy. % FIXME: update number if necessary
In the $D/P$ models these are coded as either $D$ or $P$ (uncertain/consistent with either state), in the $I/C$ models they are coded as $C$, and in the $ID/CD/CP$ models they are coded as either $CD$ or $CP$.
In the hidden state models, all species were coded as consistent with both $A$ and $B$.
}
\label{figure:stateclassifications}
\end{figure}

>>>>

Matching our character state data to the largest time-calibrated phylogeny of Solanaceae \citep{sarkinen_2013} yielded 651 species with ploidy and/or breeding system information on the tree.
% Fixed!
Of these, 368 had information for both states.
The number of species in each combination of states is summarized in \cref{figure:stateclassifications}A.
We retained all 651 species in each of the analyses below because pruning away tips lacking breeding system in the ploidy-only analyses (and vice versa) would discard data that could inform the diversification models.
A total of 372 taxa without any information about breeding system or ploidy were excluded.
%Tips without trait data might not improve point estimation of diversification parameters while increasing uncertainty in the estimates of trait linked diversification
% R-This is very important but I have removed it because I think it is a full on paper by its own
%Including this many more species would have prohibitively slowed our analyses, especially those implementing the most complex models.

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{states.pdf} % FIXME: update numbers
\caption{
Character states used for each of the models.
Each species retained on the tree belonged to one of five possible categories, depending on whether ploidy and/or breeding system were known.
(A) The five categories and the number of species in each.
Abbreviations are $I$ for self-incompatible, $C$ for self-compatible, $D$ for diploid, $P$ for polyploid, $?$ for unknown.
Because polyploidization breaks this form of self-incompatibility, SI species with unobserved ploidy ($I?$) are taken to be diploid ($ID$), and polyploid species with unobserved breeding system ($?P$) are taken to be SC.
(B) Category groupings into states for each model type.
For example, there are 70 species that are SC with unknown ploidy. % Fixed
In the $D/P$ models these are coded as either $D$ or $P$ (uncertain/consistent with either state), in the $I/C$ models they are coded as $C$, and in the $ID/CD/CP$ models they are coded as either $CD$ or $CP$.
In the hidden state models, all species were coded as consistent with both $A$ and $B$. Two species \textit{Lycium californicum} and \textit{Solanum bulbocastanum} are simultaneously ID and CP and by adding them the sample adds to the total of 651 taxa used for analyses.
}
\label{figure:stateclassifications}
\end{figure}
